Adopting agile in the large: motivations, success factors and challenges

### 2014-04-10 journal/article.tex
Explaining combining sources per case organization

@@

\subsection{Summary of papers}

>>>>

In several cases the transformation of a single organization was described in
more than one primary study. Even if the transformation of a single organization
was described in many studies all sources that passed the inclusion criterial
were included. The reason for this was that we wanted to gain as much insight
from each organization as possible. As a result 40 unique organizations were
identified in the primary studies.

@@

\subsection{Overview of primary studies}

The results of this study include findings from 52 primary studies presenting
how 40 different large organizations introduce agile software development.

Time of transformation

Organization size varied 50 -- 15000. Median.

Agile methods used
